---
title: 'Econ #1'
author: "Brad Anderson"
date: "April 5, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
 library(tidyverse)

dat <- read.csv("HW1data.csv")
colnames(dat) <- c("parcel","a","b","cost")

```

A) We will want to purchase the parcels that have the highest habitat quality values and the lowest cost. For example, parcel 1 has a low cost of of 0.1 with high habitat quality values of 3 for both species A and B. Obviously, this will result in us purchasing any value 3 parcels with low scores. Things get tricker as the value 3 parcels get more expensive. Let's say we are forced to choose to buy one value 3 parcel or two value 2 parcels, which is better? Habitat area is a factor in our function that determines the probability of survival, thus I would suspect that conserving more area of lower value will often be better.

B) We will use $Pr(survival) = c[\sqrt{\sum{w_ix_i}}]$ and then use the linearly constrained optimization (contrOptim in R) with a budget of $10 million dolars to determine how much of which parcels to purchase.

```{r function}

suitable <- function(purchases){
  
  suitability <- sqrt(sum(purchases*dat$a))
  
  return(-suitability)
}
```

```{r purchase every parcel}

every_parcel = rep(1,50)
maximum_probability = suitable(every_parcel)

C_a <- (1/maximum_probability)*-1

C_a

```


```{r}
eye = diag(50) # The identity matrix
coefs = rbind(eye, -eye, -dat$cost)

# Now we need to set up the value of the constraint, which is a vector of 50 zeros, 50 negative 1's, and finally the 
# number 10 which is the total cost (you may need to review matrix multiplication for this to make sense)

constraints = c(rep(0,50), rep(-1,50), -10)

# Lets see if it works....

initial_guess = rep(0.4,50) 

# remember the initial guess has to be feasible which you can check 
# by typing coefs %*% initial_guess >= constraints into the console & checking they are all true

output = constrOptim(initial_guess, suitable, ui=coefs, ci=constraints, grad=NULL)
```

```{r}

# You can reference the optimization output as follows

success_prob_A_only = -output$value
purchases = output$par

success_prob_A_only*C_a
purchases

dat_update = cbind(dat, purchases)



```

